Making Sequential Programs Deterministic

### 2019-03-28 experiments.tex
todo: redraw figure

\begin{itemize}
    \item Refer to table and describe it.
    \item P7: same source causing multiple tests to be flaky
    \item Example for class.GetDeclaredMethod() and show annotations
    \item Example for HashMap.entrySet() and show annotations.
    \item qualitative comparison: orthogonal techniques (reporting tests vs reporting source locations).
    \item From NonDex paper: "manually inspecting these failures was rather challenging"
\end{itemize}

\begin{table}[]
    \begin{tabular}{|p{1.5cm}|p{1cm}|p{3cm}|p{4cm}|p{2cm}|p{1.5cm}|}
        \hline
        Benchmark & Recall? & Error message source & Error msg & \#annotations & Annotation type  \\ \hline
        P1 & Yes & FieldAccess.java: [102,87] & assignment type incompatible &  &   \\
        P2 & MI &  &  &  &  \\
        P3 & Yes & DateTimeZone.java: [731,27] &  return type incompatible&  &  \\ 
        P4 & MI &  &  &  &  \\ 
        P5 & src &  &  &  &  \\ 
        P5 & src &  &  &  &  \\ 
        P6 & MI &  &  &  &  \\ 
        P6 & MI &  &  &  &  \\
        P7(test error) & Yes & checker/ tests/ determinism/P71.java: 5 & return type incompatible &  &  \\ 
        P7(2) & Yes & FieldUtils.java: [219,84] & assignment type incompatible &  &  \\
        P7(2) & Yes & Reflection ToStringBuilder.java: [543,65]  & assignment type incompatible &  &  \\
        P7(2) & Yes & HashCodeBuilder.java: [193,69]  & assignment type incompatible &  &  \\
        P7(2) & Yes & CompareToBuilder.java: [322,65] & assignment type incompatible &  &  \\
        P7(2) & Yes & EqualsBuilder.java: [419,69]  & assignment type incompatible &  &  \\
        P7 & Yes & FieldUtils.java: [200,69] & assignment type incompatible & &  \\
        P7 & Yes & FieldUtils.java: [219,84] & assignment type incompatible &  &  \\
        P7 & Yes & FieldUtils.java: [240,86] & assignment type incompatible &  &  \\
        P8 & RM &  &  &  &  \\
        P8 & RM &  &  &  &  \\
        P8 & RM &  &  &  &  \\
        P9 & MI &  &  &  &  \\
        P10 & crash &  &  &  &  \\
        P10 & crash &  &  &  &  \\
        P11 & MI &  &  &  &  \\
        P12 & MI &  &  &  &  \\
        P13 & crash &  &  &  &  \\
        P14 & MI &  &  &  &  \\
        P15 & MI &  &  &  &  \\
        P15 & MI &  &  &  &  \\
        P16 & Yes & MethodSorter.java: [56,61]  & assignment type incompatible &  &  \\
        P17 & Yes &  &  &  &  \\
        P18 & src &  &  &  &  \\
        P19 & MI &  &  &  &  \\
        P19 & MI &  &  &  &  \\
        P19 & MI &  &  &  &  \\
        P20 & MI &  &  &  &  \\
        P20 & MI &  &  &  &  \\
        P21 & MI &  &  &  &  \\
        P21 & MI &  &  &  &  \\ \hline
    \end{tabular}
\end{table}

>>>>

\begin{itemize}
    \item Refer to table and describe it.
    \item P7: same source causing multiple tests to be flaky
    \item Example for class.GetDeclaredMethod() and show annotations
    \item Example for HashMap.entrySet() and show annotations.
    \item qualitative comparison: orthogonal techniques (reporting tests vs reporting source locations).
    \item From NonDex paper: "manually inspecting these failures was rather challenging"
    \item Note: P7\_1 and P18: error in test case, so we added the same test to our microbenchmarks
\end{itemize}

\begin{table}[]
    \begin{tabular}{|p{1.5cm}|p{1cm}|p{3cm}|p{4cm}|p{2cm}|p{1.5cm}|}
        \hline
        Benchmark & Recall? & Error message source & Error msg & \#annotations & Annotation type  \\ \hline
        P1 & Yes & FieldAccess.java: [102,87] & assignment type incompatible &  &   \\
        P2 & MI &  &  &  &  \\
        P3 & Yes & DateTimeZone.java: [731,27] &  return type incompatible&  &  \\ 
        P4 & MI &  &  &  &  \\ 
        P5 & visualee &  &  &  &  \\ 
        P5 & src &  &  &  &  \\ 
        P6 & MI &  &  &  &  \\ 
        P6 & MI &  &  &  &  \\
        P7(test error) & Yes & checker/ tests/ determinism/P71.java: 5 & return type incompatible &  &  \\ 
        P7(2) & Yes & FieldUtils.java: [219,84] & assignment type incompatible &  &  \\
        P7(2) & Yes & Reflection ToStringBuilder.java: [543,65]  & assignment type incompatible &  &  \\
        P7(2) & Yes & HashCodeBuilder.java: [193,69]  & assignment type incompatible &  &  \\
        P7(2) & Yes & CompareToBuilder.java: [322,65] & assignment type incompatible &  &  \\
        P7(2) & Yes & EqualsBuilder.java: [419,69]  & assignment type incompatible &  &  \\
        P7 & Yes & FieldUtils.java: [200,69] & assignment type incompatible & &  \\
        P7 & Yes & FieldUtils.java: [219,84] & assignment type incompatible &  &  \\
        P7 & Yes & FieldUtils.java: [240,86] & assignment type incompatible &  &  \\
        P8 & RM &  &  &  &  \\
        P8 & RM &  &  &  &  \\
        P8 & RM &  &  &  &  \\
        P9 & MI &  &  &  &  \\
        P10 & crash &  &  &  &  \\
        P10 & crash &  &  &  &  \\
        P11 & MI &  &  &  &  \\
        P12 & MI &  &  &  &  \\
        P13 & crash &  &  &  &  \\
        P14 & MI &  &  &  &  \\
        P15 & MI &  &  &  &  \\
        P15 & MI &  &  &  &  \\
        P16 & Yes & MethodSorter.java: [56,61]  & assignment type incompatible &  &  \\
        P17 & Yes &  &  &  &  \\
        P18 & slf4j &  &  &  &  \\
        P19 & MI &  &  &  &  \\
        P19 & MI &  &  &  &  \\
        P19 & MI &  &  &  &  \\
        P20 & MI &  &  &  &  \\
        P20 & MI &  &  &  &  \\
        P21 & MI &  &  &  &  \\
        P21 & MI &  &  &  &  \\ \hline
    \end{tabular}
\end{table}
